Efficient Handling of String-Number Conversion

### 2020-04-04 final-version/evaluation.tex
update tables

As an addition experiment, we have encoded the checkLuhn algorithm introduced in Section~\ref{section:introduction} for the cases with 2 to 12 loops (digits). We ran these tests 
%additionally to the experiments above 
with the timeout set to 120s. The result is summarized in Table~\ref{table:checkLuhn}.
In these tests, {\tool} can solve all problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3Str3 could not solve any of these problems (either timeout or UNKNOWN). However, Z3 can still solve 7 out of the 11 problems, while timeouting in the cases with 4, 5, 7, and 9 loops. The behavior of Z3 is not entirely unexpected. All the problems are satisfiable and the solver may be lucky to guess the solution quickly. % branch with a correct model quickly.

@@

\centering
\caption{Comparison of {\tool}, CVC4, Z3, and Z3Str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.8}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
2 			& \textbf{SAT}(0.27s)  &  \textbf{SAT}(0.89s) & \textbf{SAT}(0.45s) & \textbf{ERROR} \\
3  			& \textbf{SAT}(0.29s)  &  \textbf{SAT}(1.17s) & \textbf{SAT}(0.10s) & \textbf{ERROR} \\
4 			& \textbf{SAT}(0.37s)  &  \textbf{SAT}(4.92s) & \textbf{TIMEOUT}    & \textbf{ERROR} \\
5 			& \textbf{SAT}(0.39s)  &  \textbf{SAT}(11.27s)& \textbf{TIMEOUT}    & \textbf{ERROR} \\
6 			& \textbf{SAT}(0.41s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.13s) & \textbf{UNKNOWN} \\
7 			& \textbf{SAT}(0.51s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
8 			& \textbf{SAT}(0.53s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.29s) & \textbf{ERROR} \\
9 			& \textbf{SAT}(0.63s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
10 			& \textbf{SAT}(0.69s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.48s) & \textbf{TIMEOUT} \\
11 			& \textbf{SAT}(0.71s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.36s) & \textbf{ERROR} \\
12 			& \textbf{SAT}(0.74s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.38s) & \textbf{TIMEOUT} \\ \hline
\end{tabular}}
\label{table:checkLuhn}}
\end{table}

>>>>

As an addition experiment, we have encoded the checkLuhn algorithm introduced in Section~\ref{section:introduction} for the cases with 2 to 12 loops (digits). We ran these tests 
%additionally to the experiments above 
with the timeout set to 120s. The result is summarized in Table~\ref{table:checkLuhn}.
In these tests, {\tool} can solve all problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3Str3 could not solve any of these problems (either TIMEOUT, ERROR, or UNKNOWN). However, Z3 can still solve 5 out of the 11 problems. The behavior of Z3 is not entirely unexpected. All the problems are satisfiable and the solver may be lucky to guess the solution quickly. % branch with a correct model quickly.

@@

\centering
\caption{Comparison of {\tool}, CVC4, Z3, and Z3Str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.8}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
2 			& \textbf{SAT}(0.27s)  &  \textbf{SAT}(0.17s) & \textbf{SAT}(0.11s) & \textbf{ERROR} \\
3  			& \textbf{SAT}(0.29s)  &  \textbf{SAT}(6.94s) & \textbf{SAT}(0.13s) & \textbf{ERROR} \\
4 			& \textbf{SAT}(0.37s)  &  \textbf{SAT}(4.92s) &  \textbf{SAT}(0.24s)     & \textbf{ERROR} \\
5 			& \textbf{SAT}(0.39s)  &  \textbf{SAT}(30.86s)&  \textbf{SAT}(0.13s)     & \textbf{ERROR} \\
6 			& \textbf{SAT}(0.41s)  &  \textbf{TIMEOUT}    &\textbf{TIMEOUT} & \textbf{UNKNOWN} \\
7 			& \textbf{SAT}(0.51s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
8 			& \textbf{SAT}(0.53s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT} & \textbf{ERROR} \\
9 			& \textbf{SAT}(0.63s)  &  \textbf{TIMEOUT}    &\textbf{SAT}(0.31s)  & \textbf{ERROR} \\
10 			& \textbf{SAT}(0.69s)  &  \textbf{TIMEOUT}    &  \textbf{TIMEOUT} & \textbf{TIMEOUT} \\
11 			& \textbf{SAT}(0.71s)  &  \textbf{TIMEOUT}    &  \textbf{TIMEOUT} & \textbf{ERROR} \\
12 			& \textbf{SAT}(0.74s)  &  \textbf{TIMEOUT}    &  \textbf{TIMEOUT} & \textbf{ERROR} \\ \hline
\end{tabular}}
\label{table:checkLuhn}}
\end{table}

### 2020-04-04 final-version/main.tex
fix email of Julian
update tables

\author{Julian Dolby}
\affiliation{
  \institution{IBM Research}
      \state{NY}
    \country{USA}                    %% \country is recommended
}
\email{bui.phi-diep@it.uu.se}

@@

Most of the state-of-the-art string constraint solvers provide limited support to the combination of above constraints.
\changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 fails to solve the cases corresponding to 4,5,7, and 9 loop iterations, and Z3Str3 fails to solve  the case of 2 loop iterations.}

>>>>

\author{Julian Dolby}
\affiliation{
  \institution{IBM Research}
      \state{NY}
    \country{USA}                    %% \country is recommended
}
\email{dolby@us.ibm.com}

@@

Most of the state-of-the-art string constraint solvers provide limited support to the combination of above constraints.
\changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 can only solve the cases corresponding to 2 to 5, and 9 loop iterations, and Z3Str3 fails to solve any case.}
